---
title: 'ERHS: Homework 4'
author: "Ana Velasquez Munoz"
date: "November 4, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r packages, include = FALSE}
library(knitr)
library(readr)
library(dplyr)
library(tidyr)
library(broom)
library(ggplot2)
library(ggthemes)
library(forcats)
library(scales)
library(ggthemes)

```

##Estimating the proportion of unsolved homicides in each city

1. and 2. Reading the data as an R object named homicides and creating a new column called city_name that combines the city and state

```{r loading data}
homicides <- read_csv("data-homicide/homicide-data.csv") %>% 
  unite(city_names, city, state, sep = ",")
head(homicides)

```

3. Creating a dataframe called *unsolved* with one row per city that gives the total number of homicides for the city and the number of unsolved homicides.

```{r unsolved data frame, echo = FALSE, results = 'markup'}
unsolved <- homicides %>% 
  select(city_names, disposition)%>% 
  mutate(unsolved = disposition %in% c("Closed without arrest", 
                                       "Open/No arrest")) %>% 
  group_by(city_names) %>% 
  summarize(n_homicides = n(),
            unsolved = sum(unsolved))
head(unsolved)

```

4. Baltimore prop.test and confidence interval

```{r, baltimore prop.test, echo = FALSE}

#baltimore prop test

prop.test(c(unsolved$unsolved [3]),
          c(unsolved$n_homicides[3]),
          conf.level = 0.95, correct = TRUE)

baltimore <-prop.test(c(unsolved$unsolved [3]),
          c(unsolved$n_homicides[3]),
          conf.level = 0.95, correct = TRUE)
kable(tidy(baltimore))

```

5. Prop.test all cities and confidence interval using **purrr::map2**
```{r, prop test all cities}

unsolved <- homicides %>% 
  select(city_names, disposition)%>% 
  mutate(unsolved = disposition %in% c("Closed without arrest", 
                                       "Open/No arrest")) %>% 
  group_by(city_names) %>% 
  summarize(n_homicides = n(),
            unsolved = sum(unsolved)) %>% 
  mutate(newcol = purrr::map2(unsolved, n_homicides,  
                              ~ prop.test(.x, n = .y) %>% 
                  {tibble(estimate = .[["estimate"]],
                         ci_lower = .[["conf.int"]][[1]], 
                         ci_upper = .[["conf.int"]][[2]])})) %>%
  unnest()

kable(head(unsolved))
```
6. Plot of unsolved homicides for all cities  using geom_errorbarh 

```{r, plot all cities, fig.height = 9, fig.width= 6}

unsolved %>% 
  mutate(city_names = fct_reorder(city_names, estimate)) %>% 
  ggplot() +
  geom_errorbarh(aes(y = city_names, x = estimate, xmin = ci_lower, 
                   xmax = ci_upper), height = 0, color = "white")+
  geom_point( mapping = aes(y = city_names, x = estimate), 
              size = 1, shape = 21, color = "white", fill = "white") +
  theme_dark()+
  scale_x_continuous(labels = percent)+
  labs(x = "Percent of homicides that are unsolved", y = " ")+
  ggtitle("Unsolved homicides by city",
          subtitle = "Bars show 95% confidence interval")

```


